---
title: "Word Cloud: Appointment Activities"
author: "Hector Kurtyanek"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning  = FALSE, message = FALSE)
```

## Code Summary

This code produces a simple word cloud visualisation of appointment activities

## Remove objects if necessary

```{r}
rm(list = ls())
```

### Install Packages

You will need to install the below packages to create the output

```{r}
#install.packages("tm")
```

### Make packages available

```{r}
library(tm)
```

### Give some more information on the pacakge

```{r}
#??tm
```


### Read text file into R
```{r}
TagLog_txt <- VCorpus(DirSource("H:/R/Text")) #Make sure you just read the folder path in (must only contain one text file)
```

## Text Manipulation

#### Convert to lower case
```{r}
TagLog_txt2 <- tm_map(TagLog_txt, content_transformer(tolower))
```

#### Remove punctuations
```{r}
TagLog_txt3 <- tm_map(TagLog_txt2, removePunctuation)
```

#### Remove stopwords
```{r}
TagLog_txt4 <- tm_map(TagLog_txt3, removeWords, stopwords())
```


#### Generate TF-IDF matrix
```{r}
TagLog_dtm <- DocumentTermMatrix(TagLog_txt4)
```

#### Inspect to TF-IDF
```{r}
inspect(TagLog_dtm)
```

#### Generate a frequency data frame
```{r}
word_frequency <- sort(colSums(as.matrix(TagLog_dtm)),
                       decreasing=TRUE)
df_frequency<- data.frame(word = names(word_frequency),
                          freq=word_frequency)

head(df_frequency)
```


# Displaying the Word Cloud


### Install Packages
```{r}
#install.packages("wordcloud")
```

### Make packages available
```{r}
library(wordcloud)
```

## Simple Word Cloud
```{r}
wordcloud(df_frequency$word,
          df_frequency$freq)
```



## Top 10 words
```{r}
wordcloud(df_frequency$word,
          df_frequency$freq,
          max.words=10, min.freq = 1)
```


# Enhancing the Word Cloud


### Choose a specific font and order
```{r}
wordcloud(df_frequency$word,
          df_frequency$freq,
          max.words=10, min.freq = 1,
          random.order=FALSE,
          family = "Helvatica", font = 3)
```


### Using a color palatte
```{r}
library(RColorBrewer)

word_pal <- brewer.pal(10,"Dark2")

wordcloud(df_frequency$word,
          df_frequency$freq,
          max.words=20, min.freq = 1,
          random.order=FALSE,
          colors=word_pal, font = 3)

```














